---
editor_options: 
  chunk_output_type: console
---

# Scenario 3: Mechanistic, undifferentiated competitor preferences

```{r}
# load packages
library(data.table)
library(ggplot2)
```

## Evolved, mechanistic movement with undifferentiated agent preferences on patchy resource landscapes

```{r}
# run scenarios
data_2pref <- lapply(seq(20), function(x) {
  ecoevomove2::model_case_2(
    scenario = 2,
    landsize = 30,
    nItems = 450,
    clusterSpread = 0.5,
    nClusters = 30,
    regen_time = 100,
    tmax = 400,
    handling_time = 5,
    popsize = 200,
    genmax = 100,
    dispersal = 10,
    range_perception = 1,
    mProb = 0.01,
    mSize = 0.01,
    nThreads = 2
  )
})
```

```{r}
# examine intake in evolved movement
data_2pref_intake = lapply(data_2pref, slot, "trait_data")

# assign replicate
data_2pref_intake = Map(
    data_2pref_intake, seq(length(data_2pref_intake)),
    f = function(df, n) {
        setDT(df)
        df[, replicate := as.factor(n)][]
    }
)

data_2pref_intake = rbindlist(data_2pref_intake)
data_2pref_intake = ecoevomove2::get_social_strategy(data_2pref_intake)

# add details
data_2pref_intake[, landscape := "patchy"]
data_2pref_intake[, type := "2pref"]
data_2pref_intake[, dispersal := "global"]

# save trait data
fwrite(
    data_2pref_intake,
    file = "inst/data/data_traits_2pref_patchy_global.csv"
)
```

Networks from evolved movement strategies on patchy landscapes.

```{r}
networks_2pref = lapply(data_2pref, ecoevomove2::make_network, weight_threshold = 3)

# save networks
saveRDS(networks_2pref, file = "inst/data/networks_2pref_patchy_global.Rds")
```

## Evolved, mechanistic movement with undifferentiated agent preferences on homogeneous resource landscapes

```{r}
# run scenarios
data_2pref <- lapply(seq(20), function(x) {
  ecoevomove2::model_case_2(
    scenario = 2,
    landsize = 30,
    nItems = 450,
    clusterSpread = 0.5,
    nClusters = 90,
    regen_time = 100,
    tmax = 400,
    handling_time = 5,
    popsize = 200,
    genmax = 100,
    dispersal = 10,
    range_perception = 1,
    mProb = 0.01,
    mSize = 0.01,
    nThreads = 2
  )
})
```

```{r}
# examine intake in evolved movement
data_2pref_intake = lapply(data_2pref, slot, "trait_data")

# assign replicate
data_2pref_intake = Map(
    data_2pref_intake, seq(length(data_2pref_intake)),
    f = function(df, n) {
        setDT(df)
        df[, replicate := as.factor(n)][]
    }
)

data_2pref_intake = rbindlist(data_2pref_intake)
data_2pref_intake = ecoevomove2::get_social_strategy(data_2pref_intake)

# add details
data_2pref_intake[, landscape := "homog"]
data_2pref_intake[, type := "2pref"]
data_2pref_intake[, dispersal := "global"]

# save trait data
fwrite(
    data_2pref_intake,
    file = "inst/data/data_traits_2pref_homog_global.csv"
)
```

Networks from evolved movement strategies on homog landscapes.

```{r}
networks_2pref = lapply(data_2pref, ecoevomove2::make_network, weight_threshold = 3)

# save networks
saveRDS(networks_2pref, file = "inst/data/networks_2pref_homog_global.Rds")
```
